---
title: 'Study 4 Analysis: Perceptual Adaptation'
author: "Kelsey Neuenswander"
date: "9/14/2021"
output:
  pdf_document: default
  html_document: default
---

This study investigates the social evaluative implications of sensory adaptation to men's _and_ women's voices. 

**Stimuli.** Test stimuli were audio recordings of 20 young adult men and 20 young adult women reciting the sentence "Hi, I'm a student at UCLA". Samples were recorded digitally (M-Audio Microtrack recorder, 16-bit amplitude resolution, 44.1 kHz sampling rate) using an AKG E535 condenser microphone placed approximately 15cm from the mouth. Stimuli varied naturally in duration, fundamental frequency ($f_o$), and voice quality.

**Adapting stimuli.** Adaptors included both masculinized and feminized exemplars that would be gender-typical or gender-atypical relative to test stimuli. Male adaptors were generated from recordings of 5 young adult men producing the same sentence as test stimuli. These recordings were manipulated to be more masculine or more feminine using the VT-Change script in Praat (Boersma & Weenink, 2021). We altered $f_o$, a well-established sexually dimorphic aspect of voice, using PSOLA (Pitch Synchronous Overlap Add) resynthesis. For masculinized versions, $f_o$ values were lowered to 90% of baseline. For feminized versions, $f_o$ was increased to 175% of baseline. Female adaptors were generated from recordings of 5 young adult women producing the same sentence as test stimuli. For masculinized versions, $f_o$ values were lowered to 70% of baseline. For feminized versions, $f_o$ was increased to 140% of baseline. 

**Procedure.** We recruited U.S. residents from Prolific. After providing consent, participants were randomly assigned to either a feminized or masculinized adaptation condition. In one block, participants listened to only male voices and in another block they listened to only female voices. On each trial, participants fist heard an adapting voice followed by a test voice which they judged for attractiveness and masculinity/femininity (1 = _Not at all_ to 9 = _Extremely_). We also collected perceptions of likability, friendliness, and typicality for future exploratory analyses not reported here. To maintain attention, participants also completed a secondary task rating whether the pitch of each adaptor was higher, lower, or identical to the previous adaptor. Participants completed 20 trials in pseudo-randomized order in each block (40 trials total), with each adaptor presented four times.

**Hypotheses.** Variability in vocal tract length and laryngeal cavity size create large differences in fundamental frequency for male and female voices (Hillenbrand et al., 1995). Perceivers evaluate men and women with regard to these differences, rating men as more attractive when their voices have low fundamental frequency but women as more attractive when their voices have high fundamental frequency (Puts, 2005; Puts, Barndt, Welling, Dawood, & Burriss, 2011). Therefore, we predicted that participants in the feminized adaptation condition would rate male test voices as more attractive and female test voices as less attractive than participants in the masculinized adaptation condition. Furthermore, we predicted that participants in the masculinized adaptation condition would rate male test voices as less attractive and female test voices as more attractive than participants in the feminized condition. This is because adaptation to feminized male voices or masculinized female voices will make a neutral test voice sound more typical and therefore more favorable.

```{r, message=FALSE, echo=FALSE, warning=FALSE}
library(lme4)
library(lmerTest)
library(mediation)
library(dplyr)
library(nlme)
library(ggplot2)
library(grid)
library(gridExtra)
library(pastecs)
library(mosaic)
library(scales)
library(PHEindicatormethods) 
options(scipen=999)
```

```{r, echo = F}
library(knitr)
library(formatR)
opts_chunk$set(tidy.opts=list(width.cutoff=70),tidy=TRUE)
```

**Load Data**
```{r}
data <- read.csv('study4_data.csv', header=TRUE)
```

**Factor**
```{r}
# participant ID
data$ID <- factor(data$ID)

# condition
data$condition <- as.factor(data$condition)

# target sex
data$target.sex <- as.factor(data$target.sex)

# participant sex
data$Sex <- as.factor(data$Sex)
```

**Filter**  
There were only 4 participants who did not identify as male or female. Because we were interested in investigating the interaction between condition, target sex, and participant sex, we filtered out participants who did not identify as male or female since the power for detecting an effect with a sample size of 4 is too low. 
```{r}
nrow(data)/40
data <- data %>% filter(Sex == "1" | Sex == "2")
nrow(data)/40
```

**Check Data Quality**  
Group by participant ID and filter out participants with a response range of 1 on any of the dependent variables. 
```{r}
#sample size before filtering
nrow(data)/40 # divide by number of trials since data is long form

#attraction
data <- data %>% group_by(ID) %>% 
  filter((max(attraction) - min(attraction) > 1))

#masculinity/femininity
data <- data %>% group_by(ID) %>% 
  filter((max(masc.fem) - min(masc.fem) > 1))

#likability
data <- data %>% group_by(ID) %>% 
  filter((max(likability) - min(likability) > 1))

#friends
data <- data %>% group_by(ID) %>% 
  filter((max(friends) - min(friends) > 1))

#typicality
data <- data %>% group_by(ID) %>% 
  filter((max(typicality) - min(typicality) > 1))

#sample size after filtering
nrow(data)/40
```

The original sample size was 178. After filtering participants whose responses did not meet our requirements, the final sample size is 172.

**Demographics**  
After filtering participants, calculate the demographics of the final sample.

Sex
```{r}
table(data$Sex)/40   # 1 = male, 2 = female, 3 = other 4 = prefer not to say
```

The majority of the sample is female (77.91%).

Race
```{r}
table(data$Race)/40  # 1 = Asian, 2 = Black, 3 = Latino, 4 = White, 5 = Biracial/Other, 6 = prefer not to say, 7 = Native American, 8 = Pacific Islander, 9 = Middle Eastern
```

The majority of the sample is White (59.88%).

Age
```{r}
stat.desc(data$Age)
```

The average age is 25.38 years old, with a range from 18 - 63.

# Multilevel Analyses (NCC Design) #
The following analyses are done in a stepwise fashion.

## Attraction ##

**Main Effect - Attraction by Condition (Masculinized/Feminized)**
```{r}
#reference group - masc condition
data$condition <-relevel(data$condition, ref = "masc")

# multilevel model
model.1 <- lmer(attraction ~ condition + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.1)

# 95% confidence interval
ci.1 <- confint(model.1, method="Wald", level=0.95)
ci.1

# group means
attraction_condition <- data %>% group_by(condition) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_condition
```

There is no difference in attraction ratings of test voices after adaptation to masculinized voices (*M* = 5.76, *SD* = 2.09) relative to feminized voices (*M* = 5.82, *SD* = 2.07), *t*(170) = 0.40, *p* = .692. 

**Main Effect - Attraction by Target Sex (Male/Female)**
```{r}
# reference group - female targets
data$target.sex <-relevel(data$target.sex, ref = "female")

# multilevel model
model.2 <- lmer(attraction ~ target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.2)

# 95% confidence interval
ci.2 <- confint(model.2, method="Wald", level=0.95)
ci.2

# group means
attraction_sex <- data %>% group_by(target.sex) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_sex
```

Female test voices (*M* = 6.13, *SD* = 1.94) are rated as significantly more attractive than male test voices (*M* = 5.45, *SD* = 2.15), *t*(6668) = -15.68, *p* < .001.

**Main Effect - Attraction by Participant Sex (Male/Female)**
```{r}
# reference group - female participants
data$Sex <-relevel(data$Sex, ref = "2")

# multilevel model
model.3 <- lmer(attraction ~ Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.3)

# 95% confidence interval
ci.3 <- confint(model.3, method="Wald", level=0.95)
ci.3

# group means
attraction_Sex <- data %>% group_by(Sex) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_Sex
```

There is no significant difference in attraction ratings between male participants (*M* = 6.00, *SD* = 1.99) and female participants (*M* = 5.73, *SD* = 2.10), *t*(170) = 1.50, *p* = .136.

**Interaction - Attraction by Condition (Masculinized/Feminized) and Target Sex (Male/Female)**
```{r fig.height=3, fig.width=5, fig.align="center"}
#simple effects: relevel so reference group = female
data$target.sex <-relevel(data$target.sex, ref = "female")

# multilevel model
model.4 <- lmer(attraction ~ condition * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.4)

# 95% confidence interval
ci.4 <- confint(model.4,method="Wald", level=0.95)
ci.4

# group means
attraction_CxTS <- data %>% group_by(condition, target.sex) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_CxTS

#plot with 95% CI
attraction_CxTS_plot <- data %>%
  group_by(condition, target.sex) %>%
  phe_mean(x = attraction, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "", x="Target Sex", y="Attraction", fill="Condition")

attraction_CxTS_plot 
```

The interaction between target sex and condition is significant, *t*(38) = 3.33, *p* = .002. Male test voices are rated as more attractive after adaptation to feminized voices, while female test voices are rated as more attractive after adaptation to masculinized voices. The simple effect of condition centered at female targets is not significant, *t*(199) = -1.38, *p* = .168.

**Simple Effect - Attraction by Condition (Masculinized/Feminized) when Target Sex (Male/Female) is centered at Male**
```{r}
#simple effects: relevel so reference group = male
data$target.sex <-relevel(data$target.sex, ref = "male")

model.5 <- lmer(attraction ~ condition * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.5)
```

The simple effect of condition centered at male targets is significant, *t*(199) = 2.06, *p* = .040.

**Interaction - Attraction by Condition (Masculinized/Feminized) and Participant Sex (Male/Female)**
```{r fig.height=3, fig.width=5, fig.align="center"}
#simple effects: relevel so reference group = female
data$Sex <-relevel(data$Sex, ref = "2")

# multilevel model
model.6 <- lmer(attraction ~ condition * Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.6)

# 95% confidence interval
ci.6 <- confint(model.6,method="Wald", level=0.95)
ci.6

# group means
attraction_CxPS <- data %>% group_by(condition, Sex) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_CxPS

#plot with 95% CI
attraction_CxPS_plot <- data %>%
  group_by(condition, Sex) %>%
  phe_mean(x = attraction, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=Sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "", x="Participant Sex (1 = Male, 2 = Female)", y="Attraction", fill="Condition")

attraction_CxPS_plot 
```

The interaction between condition and participant sex is not significant, *t*(168) = -0.82, *p* = .416.

**Interaction - Attraction by Participant Sex (Male/Female) and Target Sex (Male/Female)**
```{r fig.height=3, fig.width=5, fig.align="center"}
#relevel so reference group = female
data$target.sex <-relevel(data$target.sex, ref = "female")

# multilevel model
model.7 <- lmer(attraction ~ Sex * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.7)

# 95% confidence interval
ci.7 <- confint(model.7,method="Wald", level=0.95)
ci.7

# group means
attraction_PSxTS <- data %>% group_by(Sex, target.sex) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_PSxTS

#plot with 95% CI
attraction_PSxTS_plot <- data %>%
  group_by(Sex, target.sex) %>%
  phe_mean(x = attraction, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=Sex)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "", x="Target Sex", y="Attraction", fill="Participant Sex")

attraction_PSxTS_plot 
```

The interaction between participant sex and target sex is not significant, *t*(6684) = -1.01, *p* = .314.

**Three Way Interaction - Attraction by Condition (Masculinized/Feminized), Target Sex (Male/Female), and Participant Sex (Male/Female)**
```{r, fig.align='center', fig.width=7, fig.height=3}
# reference group - female participants
data$Sex <-relevel(data$Sex, ref = "2")

# multilevel model
model.8 <- lmer(attraction ~ condition * target.sex * Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.8)

# 95% confidence interval
ci.8 <- confint(model.8,method="Wald", level=0.95)
ci.8

# group means
attraction_total <- data %>% group_by(condition, target.sex, Sex) %>%
  summarize(mean = mean(attraction),
            sd = sd(attraction),
            n = n(),
            se = sd(attraction)/sqrt(n()))
attraction_total

# subset means for male and female participants
male_data <- data %>% filter(Sex == "1")
female_data <- data %>% filter(Sex == "2")

#plot with 95% CI
male_attraction_plot <- male_data %>%
  group_by(condition, target.sex) %>%
  phe_mean(x = attraction, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "Male Participants", x="Target Sex", y="Attraction", fill="Condition")

female_attraction_plot <- female_data %>%
  group_by(condition, target.sex) %>%
  phe_mean(x = attraction, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "Female Participants", x="Target Sex", y="Attraction", fill="Condition")

grid.arrange(male_attraction_plot, female_attraction_plot, nrow=1)
```

The three way interaction is not significant, *t*(6666) = 1.06, *p* = .291. 

## Masculinity/Femininity ##

**Main Effect - Masc/Fem by Condition**
```{r}
#reference group - masc condition
data$condition <-relevel(data$condition, ref = "masc")

# multilevel model
model.9 <- lmer(masc.fem ~ condition + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.9)

# 95% confidence interval
ci.9 <- confint(model.9, method="Wald", level=0.95)
ci.9

# group means
mascfem_condition <- data %>% group_by(condition) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_condition
```

There is no difference in masc/fem ratings after adaptation to feminized voices (*M* = 5.95, *SD* = 2.01) relative to masculinized voices (*M* = 5.91, *SD* = 1.90), *t*(170) = 0.341, *p* = .734.

**Main Effect - Masc/Fem by Target Sex**
```{r}
# reference group - female targets
data$target.sex <-relevel(data$target.sex, ref = "female")

# multilevel model
model.10 <- lmer(masc.fem ~ target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.10)

# 95% confidence interval
ci.10 <- confint(model.10, method="Wald", level=0.95)
ci.10

# group means
mascfem_sex <- data %>% group_by(target.sex) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_sex
```

Female test voices (*M* = 6.22, *SD* = 1.94) are rated as significantly more feminine than male test voices are rated masculine (*M* = 5.64, *SD* = 1.92), *t*(6668) = -13.98, *p* < .001.

**Main Effect - Masc/Fem by Participant Sex**
```{r}
# reference group - female participants
data$Sex <-relevel(data$Sex, ref = "2")

# multilevel model
model.11 <- lmer(masc.fem ~ Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.11)

# 95% confidence interval
ci.11 <- confint(model.11, method="Wald", level=0.95)
ci.11

# group means
mascfem_Sex <- data %>% group_by(Sex) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_Sex
```

There is no significant difference in masc/fem ratings between male participants (*M* = 6.15, *SD* = 1.83) and female participants (*M* = 5.87, *SD* = 1.98), *t*(170) = 1.69, *p* = .094.

**Interaction - Masc/Fem by Condition and Target Sex**
```{r fig.height=3, fig.width=5, fig.align="center"}
#relevel so reference group = female
data$target.sex <-relevel(data$target.sex, ref = "female")

# multilevel model
model.12 <- lmer(masc.fem ~ condition * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.12)

# 95% confidence interval
ci.12 <- confint(model.12,method="Wald", level=0.95)
ci.12

# group means
mascfem_CxTS <- data %>% group_by(condition, target.sex) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_CxTS

#plot with 95% CI
mascfem_CxTS_plot <- data %>%
  group_by(condition, target.sex) %>%
  phe_mean(x = masc.fem, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "", x="Target Sex", y="Masc/Fem", fill="Condition")

mascfem_CxTS_plot 
```

The interaction between target sex and condition is significant, *t*(38)=6.13, *p*<.001. Male test voices are rated as significantly more masculine after adaptation to feminized voices, while female test voices are rated as significantly more feminine after adaptation to masculinized voices. Furthermore, the the simple effect of condition centered at female voices is significant, *t*(201)=-2.80, *p* < .01.

**Simple Effect - Masc/Fem by Condition when Target Sex is centered at Male**
```{r}
#simple effects: relevel so reference group = male
data$target.sex <-relevel(data$target.sex, ref = "male")

# multilevel model
model.13 <- lmer(masc.fem ~ condition * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.13)
```

The effect of condition and target sex centered at male targets is also significant, *t*(201)=3.39, *p*<.001.

**Interaction - Masc/Fem by Condition and Participant Sex**
```{r fig.height=3, fig.width=5, fig.align="center"}
#relevel so reference group = female
data$Sex <-relevel(data$Sex, ref = "2")

# multilevel model
model.14 <- lmer(masc.fem ~ condition * Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.14)

# 95% confidence interval
ci.14 <- confint(model.14,method="Wald", level=0.95)
ci.14

# group means
mascfem_CxPS <- data %>% group_by(condition, Sex) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_CxPS

#plot with 95% CI
mascfem_CxPS_plot <- data %>%
  group_by(condition, Sex) %>%
  phe_mean(x = masc.fem, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=Sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "", x="Participant Sex", y="Masc/Fem", fill="Condition")

mascfem_CxPS_plot 
```

The interaction between condition and participant sex is not significant, *t*(168) = -1.04, *p* = .301.

**Interaction - Masc/Fem by Participant Sex and Target Sex**
```{r fig.height=3, fig.width=5, fig.align="center"}
#relevel so reference group = female
data$target.sex <-relevel(data$target.sex, ref = "female")

# multilevel model
model.15 <- lmer(masc.fem ~ Sex * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.15)

# 95% confidence interval
ci.15 <- confint(model.15,method="Wald", level=0.95)
ci.15

# group means
mascfem_PSxTS <- data %>% group_by(Sex, target.sex) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_PSxTS

#plot with 95% CI
mascfem_PSxTS_plot <- data %>%
  group_by(Sex, target.sex) %>%
  phe_mean(x = masc.fem, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=Sex)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "", x="Target Sex", y="Masc/Fem", fill="Participant Sex")

mascfem_PSxTS_plot 
```

The interaction between participant sex and target sex is significant, *t*(6680) = -2.24, *p* = .025. The simple effect of participant sex when target sex is centered at female is also signficant, *t*(202) = 2.26, *p* = .025.

**Simple Effect - Masc/Fem by Participant Sex when Target Sex is Centered at Male**
```{r, fig.width=5, fig.width=5, fig.align='center'}
#relevel so reference group = female
data$target.sex <-relevel(data$target.sex, ref = "male")

# multilevel model
model.16 <- lmer(masc.fem ~ Sex * target.sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.16)

# 95% confidence interval
ci.16 <- confint(model.16,method="Wald", level=0.95)
ci.16
```

The simple effect of participant sex when target sex is centered at male is not significant, *t*(202) = 0.97, *p* = .332.

**Three Way Interaction - Masc/Fem by Condition, Target Sex, and Participant Sex**
```{r, fig.align='center', fig.height=3, fig.width=7}
# reference group - female participants
data$Sex <-relevel(data$Sex, ref = "2")

# multilevel model
model.17 <- lmer(masc.fem ~ condition * target.sex * Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.17)

# 95% confidence interval
ci.17 <- confint(model.17,method="Wald", level=0.95)
ci.17

# group means
mascfem_total <- data %>% group_by(condition, target.sex, Sex) %>%
  summarize(mean = mean(masc.fem),
            sd = sd(masc.fem),
            n = n(),
            se = sd(masc.fem)/sqrt(n()))
mascfem_total

#plot with 95% CI
male_mascfem_plot <- male_data %>%
  group_by(condition, target.sex) %>%
  phe_mean(x = masc.fem, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "Male Participants", x="Target Sex", y="Masc/Fem", fill="Condition")

female_mascfem_plot <- female_data %>%
  group_by(condition, target.sex) %>%
  phe_mean(x = masc.fem, type = "full", confidence = 0.95) %>%
  ggplot(aes(x=target.sex, y=value, fill=condition)) +
  geom_bar(stat = "identity", position = "dodge", width = .90) +
  geom_errorbar(aes(ymin = lowercl, ymax = uppercl), position = position_dodge(.90), width = 0.1) +
  scale_y_continuous(limits=c(1,7), breaks=seq(1,7,by=1), oob = rescale_none) +
  scale_fill_brewer(palette = 1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        text = element_text(size = 10)) + # apply custom minimal theme
  labs(title = "Female Participants", x="Target Sex", y="Masc/Fem", fill="Condition")


grid.arrange(male_mascfem_plot, female_mascfem_plot, nrow=1)
```

The three way interaction is significant, *t*(6666) = 2.08, *p*<.05. The simple effect of target sex and condition on masc/fem ratings centered at female participants is also significant *t*(44) = -6.56, *p*<.001.

**Simple Effect - Masc/Fem by Condition and Target Sex when Participant Sex is centered at Male**
```{r}
# reference group - male participants
data$Sex <-relevel(data$Sex, ref = "1")

# multilevel model
model.18 <- lmer(masc.fem ~ condition * target.sex * Sex + (1|ID) + (1|trial), data=data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.18)

# 95% confidence interval
ci.18 <- confint(model.18,method="Wald", level=0.95)
ci.18
```

The simple effect of target sex and condition on masc/fem ratings centered at male participants is significant *t*(141) = -3.05, *p* < .003.

# Mediation #

## Multilevel Moderated Mediation - Interaction Between Condition and Target Sex on Attractiveness Mediated by Perceived Masculinity/Femininity ##

```{r}
# group data into male and female targets
male_targ_data <- data %>% dplyr::filter(target.sex == 'male')
female_targ_data <- data %>%dplyr::filter(target.sex == 'female')
```

**Relationship between perceived femininity and attraction for female targets**
```{r}
model.y <- lmer(attraction ~ masc.fem + (1|ID) + (1|trial), data=female_targ_data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.y)

#confidence interval
ci.y <- confint(model.y,method="Wald", level=0.95)
ci.y
```

**Relationship between perceived masculinity and attraction for male targets**
```{r}
model.x <- lmer(attraction ~ masc.fem + (1|ID) + (1|trial), data=male_targ_data, na.action = 'na.exclude', control=lmerControl(optimizer = "optimx", calc.derivs = FALSE, optCtrl=list(method = 'nlminb')))
summary(model.x)

#confidence interval
ci.x <- confint(model.x,method="Wald", level=0.95)
ci.x
```

**Mediation for Female Targets**
```{r}
# detach lmerTest package (will not run otherwise)
detach("package:lmerTest", unload=TRUE)

# mediator model
med.fit.fem <- lmer(masc.fem ~ condition + (1|ID),
                      data = female_targ_data)

# outcome model
out.fit.fem <- lmer(attraction ~ condition + masc.fem + (1 |ID),
                    data = female_targ_data)

# function to calculate indirect effect (ACME) and direct effect (ADE)
med.out.fem <- mediate(med.fit.fem, out.fit.fem, treat = "condition", mediator = "masc.fem",
                      sims = 1000)
summary(med.fit.fem)
summary(med.out.fem)
```

For female targets, the effect of condition on attraction ratings was fully mediated via perceived femininity. The indirect effect is -0.25 (ACME), which is significant insofar as the confidence interval does not contain zero [-0.42, -0.07]. 

**Mediation for Male Targets**
```{r}
# mediator model
med.fit.male <- lmer(masc.fem ~ condition + (1|ID),
                      data = male_targ_data)

# outcome model
out.fit.male <- lmer(attraction ~ condition + masc.fem + (1 |ID),
                    data = male_targ_data)

# function to calculate indirect effect (ACME) and direct effect (ADE)
med.out.male <- mediate(med.fit.male, out.fit.male, treat = "condition", mediator = "masc.fem",
                      sims = 1000)

summary(med.fit.male)
summary(med.out.male)
```

For male targets, the effect of condition on attraction ratings was fully mediated via perceived masculinity. The indirect effect is .36 (ACME), which is significant insofar as the confidence interval does not contain zero [0.15, 0.59]. 

